% Drawing a tree several times using the PGF 3.0 pic feature
% Authors: Kate, Ignasi
\documentclass[tikz]{standalone}
%%%<
\usepackage{verbatim}
%%%>
\begin{comment}
:Title: Drawing trees
:Tags: Random;Pic;PGF 3.0;Decorative drawings
:Author: Ignasi
:Slug: tree-pic

PGF 3.0 introduces `pic`, a "short picture" which can be inserted
in any place of a tikzpicture.

From the manual: A “pic” is a “short picture” (hence the short name...) that
can be inserted anywhere in TikZ picture where you could also insert a node.
Similarly to nodes, pics have a “shape” (called `type` to avoid confusion) that
someone has defined. Each time a pic of a specified type is used, the type’s
code is executed, resulting in some drawings to be added to the current picture.
The syntax for adding nodes and adding pics to a picture are also very similar.
The core difference is that pics are typically more complex than nodes and may
consist of a whole bunch of nodes themselves together with complex paths
joining them.

Here we use the pic feature for drawing a tree several times.

The code was written by Kate and Ignasi and published on TeX.SE.
\end{comment}
\usetikzlibrary{decorations.pathmorphing,calc,shapes,shapes.geometric,patterns}
\tikzset{
  treetop/.style = {decoration={random steps, segment length=0.4mm}, decorate},
  trunk/.style   = {decoration={random steps, segment length=2mm,
                    amplitude=0.2mm}, decorate}}

\tikzset{
   my tree/.pic={
     \foreach \w/\f in {0.3/30,0.2/50,0.1/70} {
       \fill [brown!\f!black, trunk] (-\w/2,0) rectangle +(\w,3);
     }
     \foreach \n/\f in {1.4/40,1.2/50,1/60,0.8/70,0.6/80,0.4/90} {
       \fill [green!\f!black, treetop](0,3) ellipse (\n/1.5 and \n);
     }
   }
}
\begin{document}
\begin{tikzpicture}
  \shade[bottom color=cyan!60!black, top color=blue!20!white] (0,0)
    rectangle (10,10);
  \pic at (2,2)    {my tree};
  \pic at (4,2.5)  {my tree};
  \pic at (6,1.75) {my tree};
\end{tikzpicture}
\end{document}
